Stabilization-Free Virtual Element Methods

### 2023-01-25 reports/response.tex

\item \textsf{In the proof of Lemma 12, the authors apply a discrete trace inequality to the
quantity 
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}
$$
and cite [11, (2.18)]. However, [11, (2.18)] is a continuous trace inequality and there is no justification given for why the discrete trace inequality holds in this particular case. Moreover, it is not explained how one concludes that $\|\div\boldsymbol{\phi}\|_{-1,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}$.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the proof of Lemma 4.1, the authors claim that
$$
h_K^{\frac{1}{2}}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
$$
This is a sort of discrete trace inequality and the authors justify it by citing (A.3)-(A.4) in [15]. However, it is not apparent to me how this follows from (A.3)-(A.4). Moreover, the authors conclude that “with the multiplicative trace inequality”
$$
h_K^{\frac{1}{2}}\|v\|_{0,\partial K}\lesssim h_K^{-1}\|v\|_{0,K}.
$$
Again, this is a discrete trace inequality, and it is not specified why it is valid on the virtual space $V_k(K)$. The same goes for the arguments used in the proof of Lemma 4.3.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{When introducing the nonconforming virtual element method in Section 4, the authors should give some references for NCVEM. In particular, I don’t think the space $V_k(K)$ is the classical NCVEM space (e.g. that defined in \cite{AyusodeDiosLipnikovManzini2016}). The authors should give reference to where this space is first introduced.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{It seems that the main novelty of this work is the construction of a space
\begin{align*}
\mathbb V_{k-1}^{\div}(K):=\{\boldsymbol{\phi}&\in L^2(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \\
& \boldsymbol{\phi}\cdot\boldsymbol{n}_F\in\mathbb P^{k-1}(F)\;\forall F\in\mathcal F(K), \boldsymbol{\phi}|_T\in\mathbb P_{k-1}(T)^d\;\forall T\in\mathcal T_K
\}
\end{align*}
and a computable $L^2$ projector $Q_{K,k-1}^{\div}$ onto $\mathbb V_{k-1}^{\div}(K)$ such that
$$
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\simeq \|\nabla v\|_{0,K} \quad\forall v\in V_k(K),
$$
where $V_k(K)$ is the non-conforming space defined at line 378 (or in Section 5 the authors consider the conforming space defined at line 544). This result is stated in Lemma 4.4 and its proof relies on the norm equivalence (3.32) and the set of uni-solvent DOFs (3.29)-(3.31). However, upon reading Section 3.2 for the first time, it is difficult to grasp what it is the authors are actually trying to achieve. Are all of the spaces, definitions and lemmas in Section 3.2 really necessary to prove Lemma 4.4? If so, the authors should state the main result of Lemma 4.4 in an earlier section, and leave much of the details of Section 3.2 and the proof of Lemma 4.4 to a later section so that readers can understand what the authors are trying to achieve.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In Section 4, the authors design a stabilization free NCVEM for a reaction-diffusion problem, and in section 5 a stabilization free VEM. This seems an odd choice as one does not require a Poincar\'e inequality for the coercivity of the continuous blinear form. Indeed, if
$$
a(u, v)=(\nabla u, \nabla v)_{\Omega}+\alpha (u, v)_{\Omega}
$$
with $\alpha > 0$ then it holds trivially that
$$
\|u\|_{1,\Omega}^2\leq\max(1,\alpha^{-1})a(u,u).
$$
While things mightn't be so simple at the discrete level, it would seem more
appropriate to consider a Poisson problem.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the numerical section, the authors should compare their results to standard VEM and NCVEM to highlight any benefit their approach has.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{I suggest the authors conduct a thorough proof read of the manuscript as there are many typos, grammatical errors and poorly constructed sentences.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\end{enumerate}

\section{Response to Reviewer 3}
%\smallskip \noindent {\bf Response to Reviewer 2}.

\begin{enumerate}[1.]
\item \textsf{The paper under review presents an interesting and promising idea to avoid the stabilization term in the Virtual Element Method. The procedure adopted is very general and in principle can be used in many different settings. The paper is well written and the proofs are given with appropriate details. 
The only modification I require is a more in-depth comparison with the classical stabilized version with respect to the computational cost, in the two- and three-dimensional case, by making explicit examples in cases of interest.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\end{enumerate}

\bibliographystyle{abbrv}
\bibliography{../paper}

% ----------------------------------------------------------------
\end{document}
% ----------------------------------------------------------------

### 2023-01-31 reports/response.tex

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{An important question is whether you have in mind specific occasions where stabilization free virtual elements are superior to stabilized ones. More precisely, your procedure is sensibly more expensive and complicated than that of the standard VEM: you need a simplicial tessellation of each element; you project on BDM-type polynomial spaces; the theoretical setting itself is rather involved. If there are no apparent advantages in some specific occasion, the stabilization-free approach seems to be rather lame.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
The stabilization term in virtual element methods (VEM) brings about some problems. 
\begin{enumerate}
\item 
The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
\item 
The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
\item 
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
\item The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
\item 
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
\item Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
\end{enumerate}

@@

\medskip

\item \textsf{Lines 17-18; when you discuss the results in references \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, I am not quite sure that the polynomial degree of the projection depends only on the number of vertices. In fact, in an updated version of the preprint \cite{BerroneBorioMarcon2021}, it is possible to see that also the shape of the polygon plays a role in the choice of such a polynomial degree.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. In \cite{BerroneBorioMarcon2021}, the polynomial degree $l$ should satisfy
$$
(l+1)(l+2) - \dim\mathcal{P}_l^{\textrm{ker}}(E)\geq N_E^V-1.
$$
And the dimension of $\mathcal{P}_l^{\textrm{ker}}(E)$ generally depends on the geometry of the polygon. While the authors prove that
$$
\dim\mathcal{P}_l^{\textrm{ker}}(E)\leq l(l+1)
$$
in \cite[Theorem 2]{BerroneBorioMarcon2021}. This means a sufficient condition for $l$ is 
$$
l\geq \frac{1}{2}(N_E^V-3).
$$

@@

\medskip

\item \textsf{Line 22; ``arbitrary dimension'' only refers to the nonconforming version of the scheme. Please, better highlight this fact.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have emphasized it.

@@

\medskip

\item \textsf{I appreciate the fact that you “preview” equation (1.1) in the introduction, as it is the lynchpin of the forthcoming analysis. Yet, it would be beneficial a brief comment on the hidden constants. For instance, you should state on what such constants depend on.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have presented a comment as follows: The hidden constants in (1.1) are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~2.2 for details.

@@

\medskip

\item \textsf{Lines 41-43; you should underline that the polynomial spaces onto which you project are based on a regular simplicial tessellation of the elements of the mesh.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have mentioned it.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 138; you may wish to recall the degrees of freedom of this space, even though they are well known.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have recalled it.
